Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-26 Ben_Manuscripts/transport/Outline.tex
Fixed imports and updated outlin

  There are a number of questions that we wish to answer in order to create a
  framework for studying this system in even greater detail.
  \begin{enumerate}

@@

  	Given that the pores will restrict motion of the solutes, we anticipate that 
  	transport will be hindered in some way. We want to understand the differences in
  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
  	size and chemical identity (functional groups). We will study the interactions
  	between solutes, the membrane, and water in order to determine which mechanism
  	or mechanisms dominate.

%  	are dictated by a 
%  	solute's chemical identity and if so, what interactions lead to this
%  	difference.

@@

  There are number of questions this study is not intended to answer.
  \begin{itemize}
    \item We will not study the concentration dependence of the observed
    transport rates. Although the average MSD might change with concentration,
    we are focused on the underlying interactions leading to the observed 
    transport mechanisms which we conjecture will be the same regardless of
    concentration.
    \item We will not study the chemical potential of solutes in the pores, which
    could give us a better understanding of equilibrium solute partitioning.
    However, this information will not greatly enhance our understanding of 
    mechanistic details in various membrane regions.
    \item Both of the above points will add unnecessary levels of complexity
    which can be left for a future study. 
%    \item Our work is meant as a simple starting point for studying transport
%    mechanisms in these complex LLC systems.
    \item This work is a simple starting point meant for observing the types
    of interactions which occur between isolated solutes and the membrane.
  \end{itemize}

@@

  \subsection{Molecular Dynamics Simulations}

  \subsubsection*{System Setup}

@@

  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \subsubsection*{Radial Distribution Functions}

@@

  \subsubsection*{Coordination number}

@@

  We will answer the questions posed in the introduction in a general 
  sense before addressing them with respect to specific molecules.

  % BJC: seems right to summarize overarching mechanisms observed first  
  On the timescales simulated in our study, solutes exhibit subdiffusive
  transport behavior as evidenced by their sublinear MSD curves. 
  \begin{itemize}  
	\item As an example, the MSD curve for ethanol is plotted in 
	Figure~\ref{fig:example_msd}.
  \end{itemize}

  \noindent All solutes exhibit hop diffusion, characteristic of a continuous time random walk.
  \begin{itemize}
  	\item Figure~\ref{fig:example_ztraces} shows the $z$-coordinate versus time of
  	3 representative ethanol centers of mass.
  	\item There are clear periods of entrapment separated by relatively large hops.
  	\item The length of entrapment follows a power law distribution 
  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
  	\item Power law distributed dwell times are responsible for the ageing phenomenon
  	which causes the MSD curve to decrease with increasing measurement time as longer
  	dwell times get sampled.
  \end{itemize}

  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between steps. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops that are dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  \end{itemize}

>>>>

%  There are a number of questions that we wish to answer in order to create a
%  framework for studying this system in even greater detail.
  There are a number of questions we wish to address in order to characterize
  transport in this system.
  \begin{enumerate}

@@

  	Given that the pores will restrict motion of the solutes, we anticipate that 
  	transport will be hindered in some way. We want to understand the differences in
  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
  	size, shape and chemical functionality. We will study the interactions
  	between solutes, the membrane, and water in order to determine which mechanism
  	or mechanisms dominate.

@@

  There are number of questions this study is not intended to answer.
  \begin{itemize}
    \item We will not study the concentration dependence of the observed
    transport rates. Although the average MSD might change with concentration,
    we are focused on the underlying solute-membrane interactions that lead to
    the observed transport mechanisms which we conjecture will be the same 
    regardless of concentration.
    \item We will not study the chemical potential of solutes in the pores, which
    could give us a better understanding of equilibrium solute partitioning.
    However, this information will not greatly enhance our understanding of 
    mechanistic details in various membrane regions.
    \item Both of the above points will add unnecessary levels of complexity
    which can be left for a future study. 
%    \item Our work is meant as a simple starting point for studying transport
%    mechanisms in these complex LLC systems.
    \item This work is a simple starting point meant for observing the types
    of interactions which occur between isolated solutes and the membrane.
  \end{itemize}

@@

  \subsection*{System Setup}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We adjusted the pore radius in our systems so that the right amount of water
	fits in the pores without any vacuum using \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \subsection*{Mean Squared Displacment}

  \subsection*{Radial Distribution Functions}

@@

  \subsection*{Coordination number}

@@

  We have gained a clearer picture of the general transport properties exhibited by
  this system through the collective study of all solutes. We will first answer the
  questions posed in the introduction in a general sense before addressing them with
  respect to specific molecules where exceptions occur.

  On the timescales simulated in our study, we observe subdiffusive behavior.  
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in Figure~\ref{fig:example_msd}
	and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{}\label{fig:qualitative_mechanisms}
  \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  Mathematical modeling 
  All solutes exhibit hop diffusion, characteristic of a continuous time random walk.	
  \begin{itemize}
  	\item The length of entrapment follows a power law distribution 
  	(Figure~\ref{fig:example_powerlaw}) and the distribution of hop lengths can be 
  	described with a Gaussian distribution (Figure~\ref{fig:example_hop_dist}).
  	\item Power law distributed dwell times are responsible for the ageing phenomenon
  	which causes the MSD curve to decrease with increasing measurement time as longer
  	dwell times get sampled.
  \end{itemize}

  \noindent The direction of each hop is anti-correlated to the direction of the previous hop.
  \begin{itemize}
  	\item Figure~\ref{fig:example_autocovariance} shows the autocovariance function of 
  	ethanol step vectors. % BJC: vectors because includes magnitude + direction. Better word?
  	\item The negative autocovariance at low values of k indicates anti-correlation
  	between steps. 
  	\item If solutes followed a pure CTRW mechanism, the autocovariance function would
  	decay to zero immediately.
  	\item Although the autocovariance function is relatively noise, due to the somewhat small
  	number of hops observed over the course of each solute trajectory, there is the least 
  	uncertainty at k=1, the most insightful data point. This behavior is consistent across
  	all solutes molecules. % Can put error bars on points
  	\item Therefore, we believe transport can be described as subordinated fractional Brownian
  	motion where the leading process is a CTRW with hops that are dictated by the parent
  	process, FBM.
  	\item Future publications will focus on modeling the solute's transport characteristics
  	with an sFBM model
  \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
